The ChEMBL database as Linked Open Data

### 2012-03-02 article.tex
N3 syntax for examples

The Bio2RDF project provides both resolvable Linked Data URIs using a generic Linked Data server \cite{Ansell2011}, and access to SPARQL endpoints for a range of scientific databases \cite{Belleau2008}. A number of these databases are referenced in Chembl, including Chebi, Pubmed, and both the Uniprot protein and taxonomy databases. These links are vital to provide context for users who need to query across both Chembl and its related databases. The Linked Data server used by Bio2RDF has been configured for Chembl to provide URL based services for text and link searches.

@@

@@

\begin{verbatim}
\end{verbatim}

\begin{verbatim}
\end{verbatim}

@@

\begin{tiny}
\begin{verbatim}
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2000/01/rdf-schema#label> "Bis(3-[14-Benzyl-11-(1H-indol-3-ylmethyl)-2-isobutyl-13-methyl-5-(2-methylsulfanyl-ethyl)-3,6,9,12,15,20-hexaoxo-1,4,7,10,13,16-hexaaza-bicyclo[15.2.1]icos-18-en-8-yl]-propionamide)" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2000/01/rdf-schema#subClassOf> <http://semanticscience.org/resource/CHEMINF_000000> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2002/07/owl#equivalentClass> <http://bio2rdf.org/chebi:100041> .
<http://data.kasabi.com/dataset/chembl-rdf/chemblid/CHEMBL406142> <http://www.w3.org/2002/07/owl#equivalentClass> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2002/07/owl#equivalentClass> <http://data.kasabi.com/dataset/chembl-rdf/chemblid/CHEMBL406142> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2000/01/rdf-schema#label> "CHEMBL406142" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.blueobelisk.org/chemistryblogs/smiles> "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://semanticscience.org/resource/CHEMINF_000200> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/smiles> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/smiles> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://semanticscience.org/resource/CHEMINF_000018> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/smiles> <http://semanticscience.org/resource/SIO_000300> "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.blueobelisk.org/chemistryblogs/inchi> "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://semanticscience.org/resource/CHEMINF_000200> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchi> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchi> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://semanticscience.org/resource/CHEMINF_000113> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchi> <http://semanticscience.org/resource/SIO_000300> "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2002/07/owl#equivalentClass> <http://rdf.openmolecules.net/?InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.blueobelisk.org/chemistryblogs/inchikey> "LMCOMIDLRGMFCZ-RIPOXUOASA-N" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://semanticscience.org/resource/CHEMINF_000200> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchikey> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchikey> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://semanticscience.org/resource/CHEMINF_000059> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchikey> <http://semanticscience.org/resource/SIO_000300> "LMCOMIDLRGMFCZ-RIPOXUOASA-N" .
\end{verbatim}
\end{tiny}

@@

\begin{tiny}
\begin{verbatim}
<http://data.kasabi.com/dataset/chembl-rdf/journal/j6c706049c2e08871b7c46a6528065736> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://purl.org/ontology/bibo/Journal> .
<http://data.kasabi.com/dataset/chembl-rdf/journal/j6c706049c2e08871b7c46a6528065736> <http://purl.org/dc/elements/1.1/title> "J. Med. Chem." .

<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://purl.org/ontology/bibo/Article> .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/pmid> "14695813" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://www.w3.org/2000/01/rdf-schema#seeAlso> <http://bio2rdf.org/pubmed:14695813> .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/dc/elements/1.1/date> "2004" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/volume> "47" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/issue> "1" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/pageStart> "1" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/pageEnd> "9" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/dc/elements/1.1/isPartOf> <http://data.kasabi.com/dataset/chembl-rdf/journal/j6c706049c2e08871b7c46a6528065736> .
\end{verbatim}
\end{tiny}

>>>>

The Bio2RDF project provides both resolvable Linked Data URIs using a generic Linked Data server \cite{Ansell2011}, and access to SPARQL endpoints for a range of scientific databases \cite{Belleau2008}. A number of these databases are referenced in Chembl, including Chebi, Pubmed, and both the Uniprot protein and taxonomy databases \cite{TheUniProtConsortium2010}. These links are vital to provide context for users who need to query across both Chembl and its related databases. The Linked Data server used by Bio2RDF has been configured for Chembl to provide URL based services for text and link searches.

@@

\begin{small}
\begin{verbatim}
assay:a17
 a chembl:Assay ;
 chembl:extractedFrom
  res:r11347 ;
 chembl:hasAssayType chembl:ADMET ;
 chembl:hasConfScore "7"^^xsd:int ;
 chembl:hasDescription
  "Inhibition of cytochrome P450 progesterone 15-alpha hydroxylase" ;
 chembl:hasTarget target:t100122 .
\end{verbatim}
\end{small}

\begin{small}
\begin{verbatim}
target:t1
 a chembl:Target ;
 rdfs:subClassOf pro:PR_000000001 ;
 rdfs:label "Glucoamylase" , 
  "Maltase-glucoamylase, intestinal" ;
 dc:identifier "uniprot:O43451" , "3.2.1.3" ;
 dc:title "Maltase-glucoamylase" ;
 chembl:classL1 "Enzyme" ;
 chembl:hasDescription
  "Maltase-glucoamylase, intestinal" ;
 chembl:hasKeyword "Glycosidase" , 
  "Membrane" , "Sulfation" ;
 chembl:hasTaxonomy
  <http://bio2rdf.org/taxonomy:9606> ;
 chembl:organism "Homo sapiens" ;
 = <http://bio2rdf.org/uniprot:O43451> , 
   <http://bio2rdf.org/ec:3.2.1.3> .
\end{verbatim}
\end{small}

@@

@@

\begin{tiny}
\begin{verbatim}
m41:inchikey
      a       cheminf:CHEMINF_000059 ;
      cheminf:SIO_000300 "LMCOMIDLRGMFCZ-RIPOXUOASA-N" .

m41:smiles
      a       cheminf:CHEMINF_000018 ;
      cheminf:SIO_000300 "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" .

m41:inchi
      a       cheminf:CHEMINF_000113 ;
      cheminf:SIO_000300 "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" .

chemblid:CHEMBL406142
      owl:equivalentClass mol:m41 .

mol:m41
      rdfs:label "CHEMBL406142" , "Bis(3-[14-Benzyl-11-(1H-indol-3-ylmethyl)-2-isobutyl-13-methyl-5-(2-methylsulfanyl-ethyl)-3,6,9,12,15,20-hexaoxo-1,4,7,10,13,16-hexaaza-bicyclo[15.2.1]icos-18-en-8-yl]-propionamide)" ;
      rdfs:subClassOf cheminf:CHEMINF_000000 ;
      cheminf:CHEMINF_000200
              m41:inchikey , m41:smiles , m41:inchi ;
      <http://www.blueobelisk.org/chemistryblogs/inchi>
              "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" ;
      <http://www.blueobelisk.org/chemistryblogs/inchikey>
              "LMCOMIDLRGMFCZ-RIPOXUOASA-N" ;
      <http://www.blueobelisk.org/chemistryblogs/smiles>
              "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" ;
      owl:equivalentClass <http://rdf.openmolecules.net/?InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1> , <http://bio2rdf.org/chebi:100041> , chemblid:CHEMBL406142 .
\end{verbatim}
\end{tiny}

@@

\begin{tiny}
\begin{verbatim}
journal:j6c706049c2e08871b7c46a6528065736
 a bibo:Journal ;
 dc:title "J. Med. Chem." .

res:r1
 a bibo:Article ;
 rdfs:seeAlso <http://bio2rdf.org/pubmed:14695813> ;
 dc:date "2004" ;
 dc:isPartOf journal:j6c706049c2e08871b7c46a6528065736 ;
 bibo:issue "1" ;
 bibo:pageEnd "9" ;
 bibo:pageStart "1" ;
 bibo:pmid "14695813" ;
 bibo:volume "47" .
\end{verbatim}
\end{tiny}
